raptr: Representative and Adequate Prioritization Toolkit in R

### 2016-11-26 code/rmarkdown/article.Rmd
+ minor fixes to get article to compile

"
output:
  rmarkdown::pdf_document:
    toc: false
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: preamble.tex
fontsize: 11pt
documentclass: article
bibliography: references.bib
csl: reference-style.csl
---

>>>>

"
output:
  rmarkdown::pdf_document:
    toc: false
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: preamble.tex
fontsize: 11pt
documentclass: article
subparagraph: true
bibliography: references.bib
csl: reference-style.csl
---
